---
title: "HSB2 Data Analysis"
author: "Jennifer Harrist"
output: html_notebook
---
## Introduction

**The purpose of our research is to investigate the relationship between various variables and student achievement scores in reading, math, and science More specifically, we examine (a) whether a student’s scores in reading and math are related and to what extent this relationship is influenced by socioeconomic status, (b) whether gender impacts a student’s reading and math scores, (c) whether a relationship between race and reading scores exist and to what extent this relationship is influenced by socioeconomic status. Our sample consists of 200 students from different socio-economic backgrounds (low, middle, high) and different ethnicities (White, Hispanic, African-American, Asian).**

We will begin by loading in our data and setting *SES* as a factor.
```{r}
```{r include = FALSE}

library(tidyverse)
hsb2 <- read_csv("hsb2.csv")
hsb2

SES <- factor(hsb2$ses, 
              levels = c("1", "2", "3"),
              labels = c("low", "middle" ,"high"))
```

